Integration of national demographic-disturbance relationships into local caribou population viability projections can reduce uncertainty and inform monitoring decisions

### 2024-09-13 analysis/paper/paper.Rmd
New simulation set & partial update of results.

\begin{equation}
  \dot{J}_{t} \sim \text{Binomial}(\dot{W}_t,\dot{X}_t[p_0-(p_0-p_k)(\frac{\dot{W}_t}{N_0k})^b]\frac{\dot{W}_t}{\dot{W}_t+a}).
  (\#eq:dotJ)
\end{equation}

Given the values of parameters $p_0,p_k,a,$ and $b$ used by Johnson et
al. (2020) (Table A1), recruitment rate is lowest $(0.5\dot{X}_t)$ when
$\dot{N}_t=1$, approaches a maximum of $\dot{X}_t$ at intermediate
population sizes, and declines to $0.6\dot{X}_t$ as the population
reaches carrying capacity of $k=100$ times the initial population size.
The post-juvenile female population in the next year includes both
survivors and new recruits:

>>>>

\begin{equation}
  \dot{J}_{t} \sim \text{Binomial}(\dot{W}_t,\dot{X}_t[p_0-(p_0-p_k)(\frac{\dot{W}_t}{k})^b]\frac{\dot{W}_t}{\dot{W}_t+a}).
  (\#eq:dotJ)
\end{equation}

Given the values of parameters $p_0,p_k,a,$ and $b$ used by Johnson et
al. (2020) (Table A1), recruitment rate is lowest $(0.5\dot{X}_t)$ when
$\dot{N}_t=1$, approaches a maximum of $\dot{X}_t$ at intermediate
population sizes, and declines to $0.6\dot{X}_t$ as the population
reaches carrying capacity of $k=50000$.
The post-juvenile female population in the next year includes both
survivors and new recruits:

### 2024-09-13 analysis/paper/supplement.Rmd
New simulation set & partial update of results.

|$k=100$||Carrying capacity multiplier.|

@@

The choice of priors for the random effects of year on survival and recruitment are less important because the random effects have little impact on expected population growth rate (Figs \@ref(fig:PriorAllFits) and \@ref(fig:PriorAllFitsR)). We set the prior for the coefficient of variation of survival among years $\nu_S$ to vary uniformly between sNuMin = 0.001 and sNuMax = 0.13 to match the variation among national model simulations (Fig \@ref(fig:PriorAllFits)). We set the prior for the coefficient of variation of recruitment of among years $\nu_S$ to vary uniformly between rNuMin = 0.001 and rNuMax = 0.7 to match the variation among national model simulations (Fig \@ref(fig:PriorAllFitsR)).

>>>>

|$k=50000$||Carrying capacity.|

@@

The choice of priors for interannual variation in survival and recruitment are less important because these have little impact on expected population growth rate (Figs \@ref(fig:PriorAllFits) and \@ref(fig:PriorAllFitsR)). We set the prior for the coefficient of variation of survival among years $\nu_S$ to vary uniformly between sNuMin = 0.001 and sNuMax = 0.13 to match the variation among national model simulations (Fig \@ref(fig:PriorAllFits)). We set the prior for the coefficient of variation of recruitment of among years $\nu_S$ to vary uniformly between rNuMin = 0.001 and rNuMax = 0.7 to match the variation among national model simulations (Fig \@ref(fig:PriorAllFitsR)).
